Global Optimization of the Analogue Method by Means of Genetic Algorithms

### 2015-11-02 AtmoSwing - Geoscientific Model Development/template.tex
First version of the abstract.

\begin{abstract}
% TODO: write

@@

\appendix
%\section{}    %% Appendix A

@@

>>>>

\begin{abstract}

The analogue method allows forecasting local meteorological variables of interest (predictand), such as the daily precipitation, on the basis of synoptic variables (predictors). It relies on the fact that similar meteorological influences are likely to result in similar local effects. This statistical relationship is thus based on archive of observed data, and used in order to operationally forecast the coming days, or to evaluate future conditions under a changing climate.

AtmoSwing is an open source software that implement the analogue method in a very flexible way, so that different variants can be handled dynamically, by parameterization. It is made of 3 tools: the Forecaster to perform operational forecasts, the Viewer to display the results, and the Optimizer to establish the statistical relationship between the predictand and predictors.

The Optimizer integrates the most used technique, that is a semi-automatic sequential approach, as well as Monte-Carlo analyses, and especially a global optimization technique by means of Genetic algorithms. The global optimization can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now. Indeed, it allows taking into account parameters inter-dependencies, adding new degrees of freedom, and choosing objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).

These kind of optimization techniques need however to be tailored to the problem to solve. We had to assess multiple combinations of algorithms, and even to develop new operators, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of genetic algorithms to optimize the analogue method. These recommendations are a consequent outcome of this work, as it opens new perspective for the improvement of the analogue method, and its application to new regions or to new predictands.

@@

%\appendix
%\section{}    %% Appendix A

@@

\section*{Code availability}

AtmoSwing is developed under the Mercurial distributed revision control, and the source code can be found at:

\begin{itemize}
	\item http://www.atmoswing.org
	\item https://bitbucket.org/atmoswing/atmoswing
\end{itemize}

To get access to the frozen version at the time of writing (v1.4.2), the following address can be used:

\begin{itemize}
	\item bitbucket.org/atmoswing/atmoswing/commits/tag/1.4.2
\end{itemize}

The Forecaster and the Viewer are fully available, whereas the open version of the Optimizer includes all methods but the Genetic algorithms. These are planed to be released in the future, but not at the time of writing, due to lacking documentation and necessary return on investment made by Terranum.

### 2015-11-02 Optimization - Journal of Climate/template.tex
First version of the abstract.

\abstract{The analogues method is based on a statistical relationship between synoptic atmospheric variables and local weather, which we aim at forecasting. This relationship is expressed through many parameters that are usually calibrated by means of a semi-automatic procedure. This classic calibration is relatively fast and provide acceptable results, but it has strong constraints, is made of successive steps and thus cannot handle parameters dependencies, and mainly, it cannot calibrate automatically some parameters, such as the selection of the pressure levels and the temporal windows on which the predictors are compared. In order to surpass these limitations, we assessed a global optimization technique, namely genetic algorithms, that can optimize jointly all parameters of the method and thus provide a global optimum by taking into account the parameters dependencies. Moreover, it can calibrate parameters that were previously manually assessed, and can take into account new degrees of freedom that were unthinkable before. 
These kind of optimization techniques need however to be tailored to the problem to solve. We had to assess multiple combinations of algorithms, and even to develop new operators, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of genetic algorithms to optimize the analogue method. These recommendations are the primary outcome of this work, as it opens new perspective for the improvement of the analogue method, and its application to new regions or to new predictands.
We then applied the optimizer to the Rh\^{o}e catchment in the Swiss Alps and obtained coherent results which significantly improve the performance of the forecasting by analogy. The optimizer allowed us to calibrate jointly all parameters of the method and to add a weighting of the criteria per pressure level, as well as non-overlapping spatial windows.}

@@

>>>>

\abstract{The analogues method is based on a statistical relationship between synoptic atmospheric variables and local weather, which we aim at forecasting. This relationship is expressed through many parameters that are usually calibrated by means of a semi-automatic procedure. This sequential calibration is relatively fast and provide acceptable results, but it has strong constraints, is made of successive steps and thus cannot handle parameters dependencies, and mainly, it cannot calibrate automatically some parameters, such as the selection of the pressure levels and the temporal windows on which the predictors are compared. In order to surpass these limitations, we assessed a global optimization technique, namely genetic algorithms, that can optimize jointly all parameters of the method and thus provide a global optimum by taking into account the parameters dependencies. Moreover, it can calibrate parameters that were previously manually assessed, and can take into account new degrees of freedom that were unthinkable before.

We then applied the optimizer to the Rh\^{o}e catchment in the Swiss Alps and obtained coherent results which significantly improve the performance of the forecasting by analogy. The optimizer allowed us to calibrate jointly all parameters of the method and to add a weighting of the criteria per pressure level, as well as non-overlapping spatial windows.}

@@

%TODO: complete
